Developing a preprint culture in biology

### 2013-01-27 ms.tex
minor

Scientific publishing is more diversified than ever and there are many
alternative options to submit articles before formal publications. 
Social networks such as ResearchGate can be used to submit preprints
\cite{lin12}. Also, if GitHub pushes openness further by opening the writing process,
open notebooks go even further by opening the entire scientific process
\cite{san11}.

>>>>

Scientific publishing is more diversified than ever. There are now many 
alternative options to submit articles before formal publications. For 
example, social networks such as ResearchGate can be used to submit 
preprints \cite{lin12}. Also, if GitHub pushes openness further by opening 
the writing process, open notebooks go even further by opening the entire 
scientific process \cite{san11}.
